Meta-analysis of fungicide application timing for powdery mildew management

### 2020-02-11 04_Prep_data.Rmd
Table to show when spray schedules commenced
add agricolae library

```{r load_libraries}
library(dplyr)
library(readr)
library(kableExtra)
library(ggplot2)
```

@@

@@

>>>>

```{r load_libraries}
library(dplyr)
library(readr)
library(kableExtra)
library(ggplot2)
library(agricolae)
```

@@

table(slim_PM_dat$spray_management,slim_PM_dat$fungicide_timing_1)

@@

```{r delete_this_chunk}
PM_MB_means$infected_days <- as.numeric(PM_MB_means$harvest_date - PM_MB_means$first_sign_disease)

plot(AUDPC_m ~ infected_days, data = PM_MB_means)
plot(grain_yield.t.ha. ~ infected_days, data = PM_MB_means)

PM_MB_means$harvest_date - PM_MB_means$first_sign_disease
PM_MB_means[0 > as.Date(PM_MB_means$harvest_date, format = "%Y-%m-%d")-
as.Date(PM_MB_means$first_sign_disease, format = "%Y-%m-%d"),]

# correct dates (this has been done in wrangle file but not updated yet in the data-set)
PM_MB_means[PM_MB_means$trial_ref == "mung1516/01", "harvest_date"] <- as.Date("2016-05-06", format = "%Y-%m-%d")
PM_MB_means[PM_MB_means$trial_ref == "mung1516/01", "final_assessment"] <- final_assessment = as.Date("2016-04-15", format = "%Y-%m-%d")

#curiouspw10-
```
